\cvsection{Experience}
\begin{cventries}
  \cventry
    {Instructor}
    {Coding Blocks}
    {New Delhi, India}
    {June 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Teaching and Mentoring students about programming and development practices.}
        \item {Teaching Machine Learning, Web Development and frameworks such as Flask, Django, Node.js.}
      \end{cvitems}
    }
  \cventry
    {Undergraduate Research Head}
    {Vision and Artificial Intelligence Research (VAIR) Group, DTU}
    {New Delhi, India}
    {Apr. 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Study on various domains of Machine Learning and evolving field  of representational learning.}
        \item {Implementation of robust, unsupervised feature descriptors, and research on  various Deep Learning problems.}
      \end{cvitems}
    }
  \cventry
    {Mentor}
    {Codementor}
    {New Delhi, India}
    {Dec. 2015 - Present}
    {
      \begin{cvitems}
        \item {Expert Mentor on Codementor for help in Python, Machine Learning, Django, and general programming.}
        \item {Teaching people around the world and helping the developer community to grow.}
      \end{cvitems} 
    }
  \cventry
    {Co-Founder \& Full Stack Developer}
    {Greplr}
    {New Delhi, India}
    {May. 2015 - Feb. 2016}
    {
      \begin{cvitems}
        \item {Developed a hyper-local discovery platform and service aggregation application with a scalable architecture.}
        \item {Exposed REST APIs to support android application using Flask(Python Framework) and Parse for Database backend and analytics.}
      \end{cvitems}
    }
\end{cventries}
