\cvsection{Projects}
\begin{cventries}
  \cventry
    {Machine Learning, Deep Learning, Unsupervised, Reinforcement Learning, OpenAI}
    {Deep Q-Learning and Reinforcement Learning}
    {New Delhi, India}
    {May 2016 - Jun. 2016}
    {
      \begin{cvitems}
        \item {Built Neural Network model based on RNNs and CNNs to learn various states of a game, given only input frames and rewards.}
        \item {Achieved a goal of optimizing an agent to play the games on OpenAI gym simulator and achieve human-like accuracy.}
      \end{cvitems}
    }
  \cventry
    {Machine Learning, Computer Vision, Database}
    {Tracking using multi-camera environment}
    {New Delhi, India}
    {Mar. 2016}
    {
      \begin{cvitems}
        \item {Designed a tracking interface using multiple cameras for face detection and recognition from database to know trajectory followed by a person.}
        \item {Built for surveillance tasks at public places. Prototype was presented at Code for India hackathon, at Rashtrapati Bhawan, India}
      \end{cvitems}
    }
  \cventry
    {Evolutionary Algorithms, Game Theory, Neural Networks, Optimization Techniques}
    {Library for Evolutionary Optimization Techniques}
    {New Delhi, India}
    {Dec. 2015 - Mar. 2016}
    {
      \begin{cvitems}
        \item {Built an Evolutionary Optimization Library for APIs for algorithms such as Genetic Algorithm, Particle Swarm Optimization, Differential Evolution etc.}
        \item {Designed a virtual bot to play board games while optimizing the outcomes to achieve a win (\href{https://github.com/shubham1810/Mathematical_optimization}{Link}, \href{https://github.com/shubham1810/nn_tic_tac_toe}{Link})}
      \end{cvitems}
    }
  \cventry
    {Data Science, Server}
    {Food Requirement Simulation and Prediction}
    {New Delhi, India}
    {Oct. 2015}
    {
      \begin{cvitems}
        \item {Developed a web dashboard to display data and predictions for food consumption and wastage for the NGO Akshaya Patra.}
        \item {Exposed APIs for data and Predictions using Django. The prototype won the Grand Prize award at CodeForIndia 2015 Hackathon.}
      \end{cvitems} 
    }
  \cventry
    {Computer Vision, Embedded Systems}
    {Autonomous Robot Navigation System Using Kinect}
    {New Delhi, India}
    {Mar. 2015 - May 2015}
    {
      \begin{cvitems}
        \item {Built an autonomous robot and designed it’s obstacle avoidance and navigation system using OpenCV Python library.}
        \item {Analyzed performance on various development boards (Raspberry Pi, BeagleBone Black etc.) by running and optimizing the scripts.}
        \item {Used Depth maps and pixel intensity calibrations to compute distance of multiple obstacles and calculate a feasible path.}
      \end{cvitems} 
    }
\end{cventries}
